\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}

\geometry{left=0.5in, top=0.4in, right=0.5in, bottom=0.4in}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom list environment for experiences and projects
\newenvironment{resumeList}{
  \begin{itemize}[leftmargin=0.15in, label={}]
}{
  \end{itemize}
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textit{\small(#2)} & #3 \\
    \end{tabular*}\vspace{-6pt}
}

\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Shivam Kumar Verma} \\ \vspace{4pt}
  \small \href{mailto:shivam.verma.dev00@gmail.com}{shivam.verma.dev00@gmail.com} \textbullet{} +91-9135668614 \textbullet{} \href{Portfolio}{Portfolio} \textbullet{} \href{LinkedIn}{LinkedIn} \textbullet{} \href{GitHub}{GitHub}
\end{center}

%----------SUMMARY----------
\section{Professional Summary}
\vspace{3pt}
\small{Highly motivated Software Engineer with a proven ability to develop, deploy, and optimize scalable, production-grade software solutions. Experienced in full-stack development with a strong focus on Python, JavaScript (including ReactJS), and C++, complemented by expertise in distributed systems, cloud infrastructure (AWS, Docker), and database management. Adept at evaluating and refining code for efficiency, scalability, and reliability, with practical experience in integrating and leveraging AI/ML technologies. Eager to contribute to cutting-edge AI model training initiatives and enhance enterprise-level AI-driven coding solutions.}

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Programming Languages}{: Python, JavaScript, TypeScript, C++} \\ \vspace{2pt}
    \textbf{Frameworks \& Libraries}{: Node.js, Express.js, React, Next.js, FastAPI} \\ \vspace{2pt}
    \textbf{Databases \& ORMs}{: PostgreSQL, Redis, ClickHouse, Prisma, Drizzle} \\ \vspace{2pt}
    \textbf{DevOps \& Cloud}{: Docker, AWS (EC2, S3, Lambda), Nginx, Linux, Git, CI/CD} \\ \vspace{2pt}
    \textbf{AI \& ML}{: LLM integration, Prompt engineering, Semantic search, Pinecone} \\ \vspace{2pt}
    \textbf{Tools \& Technologies}{: BullMQ, Celery, Socket.IO, NextAuth}
  }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\begin{resumeList}
    \resumeSubheading
    {klimb.io}{Nagpur, Maharashtra}
    {Software Developer Intern}{Nov 2025 – Current}
  \resumeItemListStart
    \resumeItem{Redesigned platform access control by migrating from feature flags to a credit-based usage system using PostgreSQL and middleware guards, enabling monetization of 6+ AI features and cutting complexity by ∼70\%.}
    \resumeItem{Implemented a shared global template model by restructuring the database schema and backfilling data, replacing per-tenant field duplication with zero-downtime migration and complete data integrity.}
    \resumeItem{Optimized recruiter dashboard performance by introducing precomputed, indexed data pipelines, reducing load time from 2–3 seconds to under 500ms.}
  \resumeItemListEnd
\end{resumeList}

%-----------PROJECTS-----------
\section{Projects}
\begin{resumeList}
    \resumeProjectHeading
    {CodeSM}{React, Node.js, Express.js, Redis, BullMQ, Docker, PostgreSQL, AWS EC2}{Personal Project}
  \resumeItemListStart
    \resumeItem{Engineered an asynchronous code execution engine utilizing segregated BullMQ queues and lightweight Redis payload caching, ensuring reliable high-throughput submissions with near-zero dropped jobs.}
    \resumeItem{Optimized execution performance by implementing persistent Docker containers with tmpfs mounts, reducing per-test execution time from 300ms to 5ms (∼98\% faster).}
    \resumeItem{Developed a fault-tolerant worker architecture by integrating a Dead Letter Queue for retries and a 1-hour Redis cache layer, significantly reducing database load during high-traffic spikes.}
  \resumeItemListEnd

  \resumeProjectHeading
    {Storix}{Next.js, TypeScript, FastAPI, Celery, Redis, PostgreSQL, AWS S3}{Personal Project}
  \resumeItemListStart
    \resumeItem{Decoupled PDF ingestion from processing by implementing distributed Celery workers and a Redis task queue, enabling non-blocking long-running jobs without impacting API response times.}
    \resumeItem{Offloaded file transfer from the server by generating pre-signed S3 URLs for direct client uploads, eliminating backend bottlenecks and improving upload reliability.}
    \resumeItem{Integrated a Pub/Sub and WebSocket layer to push live task updates, replacing polling with real-time job status feedback from upload through delivery.}
  \resumeItemListEnd

  \resumeProjectHeading
    {Chatterly}{Next.js, Socket.IO, Redis, PostgreSQL, Prisma, NextAuth}{Personal Project}
  \resumeItemListStart
    \resumeItem{Enabled multi-instance chat functionality by wiring Redis Pub/Sub for cross-server event propagation, ensuring consistent room state across all nodes without requiring sticky sessions.}
    \resumeItem{Implemented zero-drop room event routing by subscribing each server to dedicated Redis channels, guaranteeing message delivery under concurrent multi-user load across distributed instances.}
    \resumeItem{Secured private rooms by enforcing JWT verification and room-level authorization checks at the Socket.IO middleware layer, effectively preventing unauthorized access.}
  \resumeItemListEnd
\end{resumeList}

%-----------EDUCATION-----------
\section{Education}
\begin{resumeList}
    \resumeSubheading
    {Indian Institute of Information Technology Nagpur}{Nagpur, Maharashtra}
    {B.Tech in Computer Science and Engineering}{Nov 2022 – May 2026}
    \vspace{2pt}\\
    \small{CGPA: 7.5 | Relevant Coursework: Operating Systems, Database Management Systems, Computer Networks, Object-Oriented Programming}
\end{resumeList}

\end{document}
