\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}

\geometry{left=0.5in, top=0.4in, right=0.5in, bottom=0.4in}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom list environment for experiences and projects
\newenvironment{resumeList}{
  \begin{itemize}[leftmargin=0.15in, label={}]
}{
  \end{itemize}
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textit{\small(#2)} & #3 \\
    \end{tabular*}\vspace{-6pt}
}

\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Shivam Kumar Verma} \\ \vspace{4pt}
  \small \href{mailto:shivam.verma.dev00@gmail.com}{shivam.verma.dev00@gmail.com} \textbullet{} +91-9135668614 \textbullet{} \href{Portfolio}{Portfolio} \textbullet{} \href{LinkedIn}{LinkedIn} \textbullet{} \href{GitHub}{GitHub}
\end{center}

%----------SUMMARY----------
\section{Professional Summary}
\vspace{3pt}
\small{Highly motivated Software Developer Intern with a strong foundation in full-stack development and a keen interest in AI/ML technologies, seeking to leverage expertise in a Software Engineering Evaluator role at Turing. Proven ability to build and deploy scalable, production-grade applications using modern languages like TypeScript, JavaScript, and Python, alongside frameworks such as React and Node.js. Experienced in designing robust system architectures, optimizing performance, and integrating AI features, complemented by strong competitive programming skills for precise code analysis and problem-solving.}

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{AI \& ML}{: LLM integration, Prompt engineering, Semantic search, Pinecone} \\ \vspace{2pt}
    \textbf{Languages}{: Python, JavaScript, TypeScript, C++ (Competitive Programming)} \\ \vspace{2pt}
    \textbf{Frameworks}{: React, Node.js, Express.js, Next.js, FastAPI} \\ \vspace{2pt}
    \textbf{Databases \& ORMs}{: PostgreSQL, Redis, ClickHouse, Prisma, Drizzle} \\ \vspace{2pt}
    \textbf{DevOps \& Cloud}{: Docker, AWS (EC2, S3, Lambda), Nginx, Linux, Git, CI/CD}
  }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\begin{resumeList}
    \resumeSubheading
    {klimb.io}{Remote}
    {Software Developer Intern}{Nov 2025 – Current}
  \resumeItemListStart
    \resumeItem{Engineered a credit-based monetization system, migrating from feature flags to a robust PostgreSQL and middleware guard architecture, enabling monetization of 6+ AI features and reducing system complexity by 70\%.}
    \resumeItem{Implemented a global field template architecture by restructuring the database schema and backfilling data, ensuring zero-downtime migration and complete data integrity across all customer tenants.}
    \resumeItem{Optimized recruiter dashboard performance by developing precomputed, indexed data pipelines, decreasing load times from 2-3 seconds to under 500ms.}
  \resumeItemListEnd
\end{resumeList}

%-----------PROJECTS-----------
\section{Projects}
\begin{resumeList}
    \resumeProjectHeading
    {CodeSM}{React, Node.js, Express.js, Redis, BullMQ, Docker, PostgreSQL, AWS EC2}{Personal Project}
  \resumeItemListStart
    \resumeItem{Developed a scalable asynchronous code execution engine utilizing segregated BullMQ queues and Redis payload caching, ensuring reliable high-throughput submissions with near-zero job drops.}
    \resumeItem{Enhanced execution efficiency by implementing persistent Docker containers with tmpfs mounts, reducing per-test execution time from 300ms to 5ms (98\% improvement).}
    \resumeItem{Strengthened job processing fault tolerance with a Dead Letter Queue for retries and a 1-hour Redis cache layer, significantly reducing database load during peak traffic.}
  \resumeItemListEnd

  \resumeProjectHeading
    {Storix}{Next.js, TypeScript, FastAPI, Celery, Redis, PostgreSQL, AWS S3}{Personal Project}
  \resumeItemListStart
    \resumeItem{Designed and implemented an asynchronous PDF processing pipeline using distributed Celery workers and a Redis task queue, enabling non-blocking long-running jobs without impacting API response times.}
    \resumeItem{Streamlined file uploads by integrating pre-signed AWS S3 URLs for direct client uploads, eliminating backend bottlenecks and enhancing upload reliability.}
    \resumeItem{Implemented real-time job status updates via a Pub/Sub and WebSocket layer, providing instant user feedback from upload to delivery.}
  \resumeItemListEnd

  \resumeProjectHeading
    {Chatterly}{Next.js, Socket.IO, Redis, PostgreSQL, Prisma, NextAuth}{Personal Project}
  \resumeItemListStart
    \resumeItem{Architected a horizontally scalable messaging platform by integrating Redis Pub/Sub for cross-server event propagation, ensuring consistent room state across distributed instances.}
    \resumeItem{Ensured zero message drops under concurrent multi-user loads by isolating room traffic through dedicated Redis channels across distributed instances.}
    \resumeItem{Secured private chat rooms by implementing JWT verification and room-level authorization checks within the Socket.IO middleware, preventing unauthorized access.}
  \resumeItemListEnd
\end{resumeList}

%-----------EDUCATION-----------
\section{Education}
\begin{resumeList}
    \resumeSubheading
    {Indian Institute of Information Technology Nagpur}{Nagpur, Maharashtra}
    {B.Tech in Computer Science and Engineering | CGPA: 7.5}{Nov 2022 – May 2026}
    \vspace{2pt}\\
    \small{Relevant Coursework: Operating Systems, Database Management Systems, Computer Networks, Object-Oriented Programming}
\end{resumeList}

\end{document}
