\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}

\geometry{left=0.5in, top=0.4in, right=0.5in, bottom=0.4in}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom list environment for experiences and projects
\newenvironment{resumeList}{
  \begin{itemize}[leftmargin=0.15in, label={}]
}{
  \end{itemize}
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textit{\small(#2)} & #3 \\
    \end{tabular*}\vspace{-6pt}
}

\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Shivam Kumar Verma} \\ \vspace{4pt}
  \small \href{mailto:shivam.verma.dev00@gmail.com}{shivam.verma.dev00@gmail.com} \textbullet{} +91-9135668614 \textbullet{} \href{Portfolio}{Portfolio} \textbullet{} \href{LinkedIn}{LinkedIn} \textbullet{} \href{GitHub}{GitHub}
\end{center}

%----------SUMMARY----------
\section{Professional Summary}
\vspace{3pt}
\small{Highly motivated Software Developer Intern with a strong foundation in Python, JavaScript, TypeScript, React, and C++, eager to contribute to cutting-edge AI initiatives. Proven ability to design, develop, and deploy scalable, production-grade full-stack applications and optimize backend services. Possesses a deep understanding of software architecture, data pipelines, and AI/ML integration, with hands-on experience in evaluating and refining code for efficiency, scalability, and reliability. Adept at collaborating with cross-functional teams to enhance AI-driven coding solutions and build automated verification tools, aligning with Turing's mission to advance large language models.}

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, JavaScript, TypeScript, C++} \\ \vspace{2pt}
    \textbf{Frameworks \& Libraries}{: React, Node.js, Express.js, Next.js, FastAPI} \\ \vspace{2pt}
    \textbf{Databases \& ORMs}{: PostgreSQL, Redis, ClickHouse, Prisma, Drizzle} \\ \vspace{2pt}
    \textbf{DevOps \& Cloud}{: Docker, AWS (EC2, S3, Lambda), Nginx, Linux, Git, CI/CD} \\ \vspace{2pt}
    \textbf{AI \& ML}{: LLM integration, Prompt engineering, Semantic search, Pinecone}
  }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\begin{resumeList}
    \resumeSubheading
    {klimb.io}{Nagpur, Maharashtra}
    {Software Developer Intern}{Nov 2025 – Current}
  \resumeItemListStart
    \resumeItem{Architected and implemented a credit-based monetization system for 6+ AI features using PostgreSQL and middleware, significantly reducing system complexity by 70\% and enabling new revenue streams.}
    \resumeItem{Engineered a zero-downtime database migration to a shared global template architecture, restructuring the DB schema and backfilling data to ensure complete data integrity across all customers.}
    \resumeItem{Optimized recruiter dashboard performance by introducing precomputed, indexed data pipelines, slashing load times from 2-3 seconds to under 500ms, enhancing efficiency and user experience.}
  \resumeItemListEnd
\end{resumeList}

%-----------PROJECTS-----------
\section{Projects}
\begin{resumeList}
    \resumeProjectHeading
    {CodeSM}{React, Node.js, Express.js, Redis, BullMQ, Docker, PostgreSQL, AWS EC2}{Personal Project}
  \resumeItemListStart
    \resumeItem{Developed a scalable asynchronous code execution engine by implementing segregated BullMQ queues and lightweight Redis payload caching, enabling reliable high-throughput submissions with near-zero dropped jobs.}
    \resumeItem{Optimized code execution efficiency by switching to persistent Docker containers with tmpfs mounts, reducing per-test execution time by 98\% (from 300ms to 5ms), enhancing system performance for benchmarking.}
    \resumeItem{Hardened job processing with a Dead Letter Queue for retries and a 1-hour Redis cache layer, significantly reducing database load during high-traffic spikes and improving fault tolerance.}
  \resumeItemListEnd

  \resumeProjectHeading
    {Storix}{Next.js, TypeScript, FastAPI, Celery, Redis, PostgreSQL, AWS S3}{Personal Project}
  \resumeItemListStart
    \resumeItem{Designed and implemented an asynchronous PDF processing pipeline using distributed Celery workers and a Redis task queue, decoupling ingestion from processing to maintain non-blocking API response times.}
    \resumeItem{Offloaded file transfer from the backend by generating pre-signed S3 URLs for direct client uploads, eliminating server bottlenecks and improving upload reliability for large files.}
    \resumeItem{Integrated a Pub/Sub and WebSocket layer to push real-time task updates, providing users with instant feedback from file upload through delivery.}
  \resumeItemListEnd

  \resumeProjectHeading
    {Chatterly}{Next.js, Socket.IO, Redis, PostgreSQL, Prisma, NextAuth}{Personal Project}
  \resumeItemListStart
    \resumeItem{Enabled horizontally scalable messaging across multiple instances by wiring Redis Pub/Sub for cross-server event propagation, ensuring consistent room state without sticky sessions.}
    \resumeItem{Implemented zero-drop room event routing by subscribing each server to dedicated Redis channels, guaranteeing message delivery under concurrent multi-user loads across distributed instances.}
    \resumeItem{Secured private rooms by enforcing JWT verification and room-level authorization checks at the Socket.IO middleware layer, preventing unauthorized access.}
  \resumeItemListEnd
\end{resumeList}

%-----------EDUCATION-----------
\section{Education}
\begin{resumeList}
    \resumeSubheading
    {Indian Institute of Information Technology Nagpur}{Nagpur, Maharashtra}
    {B.Tech in Computer Science and Engineering}{Nov 2022 – May 2026}
    \vspace{2pt}\\
    \small{CGPA: 7.5 | Relevant Coursework: Operating Systems, Database Management Systems, Computer Networks, Object-Oriented Programming}
\end{resumeList}

\end{document}
